API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
Write in plain letter what is rbf

In most machine learning tasks, data is modeled as a set of variables.  For
example in supervised learning task, the goal is to find a mapping
between input variables $X_1, ..., X_p$, called features, and
some discrete as in classification task or continous as in regression task
output variables $Y$. A sample is then defined as a pair of
values $([x_1,..., x_p]^\mathrm{T}, y)$ of these variables. A widely used
representation of a dataset, a collection of
such samples, is a pair of matrices with numerical values: one for the input
values and one for the output values. Each row of these matrices
corresponds to one sample of the dataset and each column to one variable of
the problem.

@@

Recent years have witnessed a rising interest in machine learning and data mining
with applications in many fields.
With this rise comes a host of machine learning packages
(both open source and proprietary) with which \sklearn competes.
Although it can also be used through its Java API, Weka \citep{hall2009weka} is
popularly used through its graphical user interface (GUI). The target audience
of the \sklearn is capable of programming, and therefore we focus on developing
a usable and consistent API, rather than expend effort into creating a GUI. In
addition, running machine learning through a GUI makes reproducibility difficult
(although Weka has developed a GUI for managing such workflows).

Other existing machine learning packages
such as SofiaML\footnote{\url{http://code.google.com/p/sofia-ml/}}
and Vowpal~Wabbit\footnote{\url{http://hunch.net/$\sim$vw/}}
are intended to be used as command-line tools
(and sometimes do not offer any type of API).
While these packages have the advantage
that their users are not tied to a particular programming language,
the users will find that they still need programming to process input/output,
and will do so in a variety of languages.
The focus of \sklearn to incorporate the entire package into a single package still
allows for the use of external tools to process input/output, however gives the added
benefit of being able to run these processes within the same development environment.
In addition, this makes it easier for researchers and developers
to exchange and collaborate on software, as dependencies and setup are kept to a
minimum.

>>>>

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, \ldots X_p$, called features, and
some output variable $Y$. A sample is then defined as a pair of
values $([x_1, \ldots, x_p]^\mathrm{T}, y)$ of these variables. A widely used
representation of a dataset, a collection of
such samples, is a pair of matrix with numerical values: one for the input
values and one for the output values. Each row of these matrix
corresponds to one sample of the dataset and each column to one variable of
the problem.

@@

Recent years have witnessed a rising interest in machine learning and data mining
with applications in many fields.
With this rise comes a host of machine learning packages
(both open source and proprietary) with which \sklearn competes.
Although it can also be used through its Java API, Weka \citep{hall2009weka} is
popularly used through its graphical user interface (GUI). The target audience
of the \sklearn is capable of programming, and therefore we focus on developing
a usable and consistent API, rather than expend effort into creating a GUI\@. In
addition, running machine learning through a GUI makes reproducibility difficult
(although Weka has developed a GUI for managing such workflows).

Other existing machine learning packages
such as SofiaML\footnote{\url{http://code.google.com/p/sofia-ml/}}
and Vowpal~Wabbit\footnote{\url{http://hunch.net/$\sim$vw/}}
are intended to be used as command-line tools
(and sometimes do not offer any type of API).
While these packages have the advantage
that their users are not tied to a particular programming language,
the users will find that they still need programming to process input/output,
and will do so in a variety of languages.
The focus of \sklearn to incorporate the entire process into a single package still
allows for the use of external tools to process input/output, however gives the added
benefit of being able to run these processes within the same development environment.
In addition, this makes it easier for researchers and developers
to exchange and collaborate on software, as dependencies and setup are kept to a
minimum.
